Computer Science House Constitution

### 2025-02-04 constitution.tex

\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.

@@

\asubsection{Honorary and Advisory Membership Term}
Honorary and Advisory Memberships shall last until the member resigns.

>>>>

\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all current members of the RIT professional, academic, or administrative staff.

@@

\asubsection{Honorary Membership Term}
Honorary Membership shall last until the member resigns.

\asubsection{Advisory Membership Term}
Advisory Membership shall last until the member resigns or is no longer employed by RIT, whichever comes first.
